Programming Language Survey Paper on Haskell

### 2013-04-21 projects/term_paper/paper.tex
Final update for 4/20
Added module code example.

If the context does not suggest the type, as in the example below, then an exception will result.

@@

\subsubsection{Modules}

\subsubsection{Exception Handling}

>>>>

If the context does not suggest the type, as in the example below, then an exception will result because the compiler cannot infer what the type is going to be and is unable to handle it.

@@

\subsubsection{Modules}
\begin{minted}{haskell}
module addNums
( addTwo
, addThree
, addFour
) where

addTwo :: (Num a) => a -> a
addTwo x = x + 2

addThree :: (Num a) => a -> a
addThree x = x + 3

addFour :: (Num a) => a -> a
addFour x = x + 4
\end{minted}
\subsubsection{Exception Handling}
